---
title: ""
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---
<style>
/* define new fonts */
@font-face {
font-family: 'Neris Thin';
font-style: normal;
font-weight: normal;
src: local('Neris Thin'), url('Neris-Thin.woff') format('woff');
}
@font-face{
    font-family: 'TheArtist';
    src: local('TheArtist'), url("TheArtist.woff") format("woff");
}
span.font1{font-family:"TheArtist";font-size:40px;text-transform:none;}

/* define colors for navigation bar */
.navbar, [data-toggle=tab], .navbar-brand{ 
  background-color:#003366!important; 
  border-color:#003366; 
  color:white!important;
  font-size: 16pt;
  display: inline-block;
  font-family: Neris Thin;
}

/* define colors for current tab */
.navbar-nav > .active > a {
  background-color:#003366!important;
  border-color:#003366;
  color:#b76e79!important;
  font-size: 16pt;
  display: inline-block;
  font-family: Neris Thin;
  font-weight: bold;
}
/* define colors for hovering */
.navbar-nav li a:hover {
  background-color:#003366!important;
  border-color:#003366;
  color:#b76e79!important;
  font-size: 16pt;
  display: inline-block;
  font-family: Neris Thin;
}
/* define colors for something */
.bgred {
  background-color:white !important;
  color:white !important;
}
body{
  text-align: center;
  width: 900px;
  margin: auto;
  font-size: 14pt;
  font-family: Neris Thin;
}

h3{
  color: #003366;
  font-size: 24pt;
}
h4{
  font-style: normal;
  font-size: 24pt;
  color: #003366;
  font-family: Neris Thin;
}
h5{
  font-size: 96pt;
  color: #b76e79;
  font-family: TheArtist;
}
h6{
  font-style: normal;
  font-size: 18pt;
  color: #003366;
  font-family: Neris Thin;
}
.nobullet li {
  list-style-type: none;
  font-size: 14pt;
  color: gray;
  font-family: Neris Thin;  
}

</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(htmltools)
library(gallerier)
```

Home
================================================

<br>

```{r Home, child = 'Home.Rmd', eval = TRUE}
```


<!-- Events {data-orientation=columns} -->
<!-- ======================================================================= -->

<!-- #### Events -->

<!-- <br> -->
<!-- <br> -->

<!-- ```{r Events, child = 'Events.Rmd', eval = TRUE} -->

<!-- ``` -->

Details
=======================================================================

#### Details

<br>
<br>

```{r Travel, child = 'Travel.Rmd', eval = TRUE}


```


Registry
=======================================================================

#### Wedding Registry

<br>
<br>

We are registered at [Amazon.com](https://www.amazon.com/wedding/share/TheLuckettest){target="_blank"} and [Crate & Barrel](https://www.crateandbarrel.com/gift-registry/crystal-nguyen-and-daniel-luckett/r6097152){target="_blank"}. 

As much as we love opening a beautifully wrapped gift, we ask that there be no boxed gifts at the wedding. It sure would be difficult to bring gifts home with us to Boston! Both registries will allow you to ship directly to us. A box will be available at the reception for any cards.


RSVP
=======================================================================

#### Répondez S'il Vous Plaît

<br>
<br>

Did you know RSVP stood for that?

```{r, echo=FALSE}
htmltools::tags$iframe(
    src="RSVP.html",
    width="750", 
    height="1600",
    seamless="seamless", 
    frameBorder="0"
  )
```

Gallery
=======================================================================

#### Gallery

<br>
<br>

```{r Gallery, child = 'Gallery.Rmd', eval = TRUE}

```

FAQs
=======================================================================

#### Frequently Asked Questions

<br>
<br>

```{r FAQ, child = 'FAQ.Rmd', eval = TRUE}
```

DIY Wedding Blog
=======================================================================

#### A Do It Yourself Wedding Blog

<br>
<br>

```{r Blog, child = 'Blog.Rmd', eval = TRUE}
```

<br>
<br>
<br>
<br>


